A Recipe for Scavenging - the natural history of a behaviour

### 2016-03-31 natural history of scavenging.tex
stegosaurus figure

\begin{abstract}
 Scavengers existed in the past and they exist now. 
 Often under appreciated. 
 Three main habitat types considered: land, air and sea. 
 Different drivers in these areas. 
 Review looks at these 
\end{abstract}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Summary_figure/Summary_figure.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. Blue lines indicates a reduction in the factor and red lines indicates an increase.}
%TG: Probably needs some more explanations...
\label{Summary_figure}
\end{figure}

>>>>

\begin{abstract}
Despite its prevalence cavenging is a difficult behaviour to observe in modern day carnivores. Yet, there are certain intrinsic and environmental features of a speices that push it towards a scavenging lifestlye. Chief among these are low-cost locomotion, high detection distances, effective carrion processing and a carrion producing environment. 
\end{abstract}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Summary_figure/Summary_figure_Landscape.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. Blue lines indicates a reduction in the factor and red lines indicates an increase.}
%TG: Probably needs some more explanations...
\label{Summary_figure}
\end{figure}
